HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-10 paper/main.tex
annotation stats

For the annotation of the machine translation, we recruited seven annotators, two for each of the target languages apart from Czech. They were
all native speakers of the target languages and fluent in English. For Czech, we also recruited a  group of additional annotators
to annotate small numbers of sentences each for the purpose of calculating inter-annotator agreement. In \tabref{tab:annot}
we show the total number of sentences and nodes annotated by each annotator, where we consider the additional Czech
annotators as a single annotator.

\emph{Show numbers of annotations, and timings}

@@

\subsection{Data}\label{sec:data}

\subsection{Efficiency of Annotation}\label{sec:efficiency}

\subsection{Inter-Annotator Agreement}
\begin{itemize}
  \item Multiple annotation stats
  \item Kappas -- ROG, AB
  \item Kappa versus length
  \item Kappa versus bleu?
\end{itemize}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes. We only consider nodes where there are at least two annotations from different
annotators and we treat nodes with more than two annotations as a set of paired
annotations\bh{This may not be correct, so should/could we do Kappa across the 
variable multiple annotations on Czech}. We consider Kappa separately on the lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad) since there should not be any confusion between these two types of
nodes. The small number of nodes which one annotator had labelled as structural and 
the other as lexical were ignored for the purposes of IAA, since such cases of annotator 
error could be caught by improved tool support.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & & 102 & 334 & 217 \\
\hline
Lexical nodes & & 1724 & 5386 & 3570 \\
Kappa & & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & & 1040 & 2655 & 1989 \\
Kappa & & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

>>>>

For the annotation of MT output, we recruited seven annotators, two for each of the target languages apart from Czech. They were
all native speakers of the target languages and fluent in English. For Czech, we also recruited a  group of additional annotators
to annotate small numbers of sentences each for the purpose of calculating inter-annotator agreement. In \tabref{tab:annot}
we show the total number of sentences and nodes annotated by each annotator, where we consider the additional Czech
annotators as a single annotator. Note that not all nodes in all sentences were annotated. Sometimes this was because the
annotator did not finish a node, or accidentally missed a node, but in many cases it was also because it was an implicit 
UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & -- & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & -- & 2906  & 9303  & 9228  \\
\end{tabular}
}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
\end{center}
\end{table}

\emph{Timing of annotations}

@@

%\subsection{Data}\label{sec:data}

%\subsection{Efficiency of Annotation}\label{sec:efficiency}

\subsection{Inter-Annotator Agreement}
\label{sec:iaa}
\begin{itemize}
  \item Multiple annotation stats
  \item Kappas -- ROG, AB
  \item Kappa versus length
  \item Kappa versus bleu?
\end{itemize}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes. We only consider nodes where there are at least two annotations from different
annotators and we treat nodes with more than two annotations as a set of paired
annotations\bh{This may not be correct, so should/could we do Kappa across the 
variable multiple annotations on Czech}. We consider Kappa separately on the lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad) since there should not be any confusion between these two types of
nodes. The small number of nodes which one annotator had labelled as structural and 
the other as lexical were ignored for the purposes of IAA, since such cases of annotator 
error could be caught by improved tool support.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & -- & 102 & 334 & 217 \\
\hline
Lexical nodes & -- & 1724 & 5386 & 3570 \\
Kappa & -- & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & & 1040 & 2655 & 1989 \\
Kappa & -- & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}
